---
title: "bighw"
author: "Chenyi Lin"
date: "2/28/2021"
output: github_document
---

```{r}
library(tidyverse)
library(nycflights13)
library(ggplot2)
```

####Question: What time of day should you fly if you want to avoid delays as much as possible? Arrive delay.  
Overview:time of the day  
```{r}
time <- flights%>%
  group_by(hour)%>%
  summarise(time_mean=mean(dep_delay,na.rm = TRUE))

```

```{r}
ggplot(time, aes(hour,time_mean))+
  geom_point()
```

Introduction:  
Withouting relating any factors(flights, airplane...), if you want to avoid delay as less as possible, you can choose to take the flight between 5:00am-12:00pm, between thsi peried, the average of flights'delay are less than 10 minutes.  

####1. carrier
Introduction:  
In overview, we already known the time between 5-12 in the morning has the less delay time. So, in part 1, I want to know which airlines that we should choose at these period.  

```{r}
carrierf<- flights%>%
  filter(hour>=5|hour<=10)%>%
  group_by(carrier)%>%
  summarise(mean_dep_delay=mean(dep_delay,na.rm = TRUE))
```
```{r}
ggplot(carrierf,aes(x=mean_dep_delay,y=carrier))+
  geom_point()
```
##summary:  
In the period 5-12 in the morning, we can choose AS,HA, and Us airlines.These only delay abut 5 minutes.   

####2. airports   
Same as part 1. We already known the time between 5-12 in the morning has the less delay time. So, in part 1, I want to know which airports that we should choose at these period.   

```{r}
flights%>%
  filter(hour>=5|hour<=10)%>%
  group_by(origin)%>%
  summarise(mean_dep_delay=mean(dep_delay,na.rm = TRUE))
```
##Summary:  
In the period 5-12 in the morning, there is no big differnce between the three origins' means of the delay time. But the flights at LGA has the less delay time, whcih is 12.3 minutes.  

####3. Weather:  
Same as before. We already known the time between 5-12 in the morning has the less delay time. So, in part 3, how temperature affect delay time.  
```{r}
flights2 <- flights %>%
  left_join(weather)
flights2
```
```{r}
flights3 <- flights2%>%
  filter(hour>=5|hour<=10)%>%
  group_by(temp)%>%
  summarise(mean_dep_delay=mean(dep_delay,na.rm = TRUE))
```
```{r}
ggplot(flights3,aes(x=temp,y=mean_dep_delay))+
  geom_point()
```
##Summary:  
From the plot,In the period 5-12 in the morning, we can find that when the temperature is around 50 Fahrenheit, the delay time is less.  
